Approximate State Abstraction

### 2016-01-26 paper/paper.tex
davellis started fully outlining section 4, including theorem 1, and the structure of the remaining lemmas

%Acronyms -- use \ac for acronym or \acp for plural/capitalization of acronym
\begin{acronym}
\acro{MDP}{Markov Decision Process}
\acrodefplural{MDP}[MDPs]{Markov Decision Processes}
\acro{RL}{reinforcement learning}
\acrodefplural{RL}{RL}{Reinforcement learning}
\end{acronym}

@@

\subsection{Exact Abstraction Framework}

@@

@@

% Subsections for proofs for each phi
\dnote{Insert lemma for each phi as their subsection, maybe with proof sketch but likely just dump in appendix.}

% Subsection:

% Subsection: Phi_Q
\subsection{$\phi_{Q^*}$}

% Subsection: Phi_M
\subsection{$\phi_{model}$}

% Subsection: Phi_{Mult}
\subsection{$\phi_{mult}$}

% Subsection: Phi_B
\subsection{$\phi_{bolt}$}

>>>>

%Acronyms -- use \ac for acronym or \acp for plural/capitalization of acronym
\begin{acronym}
\acro{MDP}{Markov Decision Process}
\acrodefplural{MDP}[MDPs]{Markov Decision Processes}
\acro{RL}{reinforcement learning}
\acrodefplural{RL}{Reinforcement learning}
\end{acronym}

@@

% Subsection: Exact Abstraction Framework
\subsection{Exact Abstraction Framework}

@@

% INTRO PARAGRAPH, setup + structure

\dnote{Explain the notation so like the $\phi_f$}

\dnote{Tee up other stuff/ideas}

% Main theorem:

\dnote{I wish this theorem used the term approximate somewhere (i.e. was using the same terminology as the intro/abstract)}
{\bf Theorem 1:} There exist at least four classes of functions on state spaces that induce abstract MDPs such that:
\begin{equation}
\forall_{s_1, s_2 \in S_G} \phi_f(s_1) = \phi_f(s_2) \rightarrow \forall_a  |f(s_1,a) - f(s_2,a)| \leq \epsilon
\end{equation}

Where, the MDP induced by the abstraction function, when solved, provides the policy $\pi^*_A$, such that:
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon)
\end{equation}

\dnote{Possible note about what all 4 functions are}

% Subsection: Optimal Q Function
\subsection{Optimal Q Function: $\phi_{Q^*}$}

\dnote{Plan to put full Q proof}

% Subsection: Model Similarity
\subsection{Model Similarity: $\phi_{model}$}

\dnote{Proof sketch}

% Subsection: Multinomial over Optimal Q
\subsection{Multinomial over Optimal Q: $\phi_{mult}$}

\dnote{Proof sketch}

% Subsection: Boltzmann over Optimal Q
\subsection{Boltzmann over Optimal Q: $\phi_{bolt}$}

\dnote{Comment about similarity to Multinomial.}

\dnote{(Probably put full proofs in appendix if we have room?}

% There are at least four classes of functions:
% 1 \phi_q^*
% 2 \phi_model
% 3 \phi_mult
% 4 \phi_bolt

@@
